Distributional State Aggregation

### 2020-03-16 minutia/paper/paper.tex
paper: clustering for aggregation added

    The original states with the closest \textit{calculated} values forgather to build aggregate states.
    For this purpose, state values are clustered by K-means analysis to calculate the relevant aggregate states.

>>>>

    \subsection{Aggregation}
    The original states with the closest \textit{calculated} values forgather to build aggregate states.
    For this purpose, state values are clustered by K-means analysis to calculate the relevant aggregate states.
    State aggregation merge similar transitions based on a triple $<s, s', a>$ where $s$ indicates the starting state,
    $s'$ is the ending state, and the take action in that transition represented by $a$.
    In the process of stacking similar transitions, we here presume all inbound transitions as outbound transition of
    the ending state.
    This assumption render all transitions as outbound ones.
